fdcoexist

### 2018-08-23 paper_simulations.Rmd
:sparkles: Add scenario RA1090 + reorder scenarios

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios,
                                time = 150) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios,
               time = time) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .))
}

@@

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    RA2575   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    RA5050   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    RA7525   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    RA100100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

trait_scenar_names = c(
    RA2575 = "Growth = 25%\nCompet. = 75%",
    RA5050 = "Growth = 50%\nCompet. = 50%",
    RA7525 = "Growth = 75%\nCompet. = 25%",
    RA100100 = "Growth = 100%\nCompet. = 100%"
)

@@

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_landscape = fig_ind_landscape(no_compet_no_cor_var_df,
                                                           no_compet_no_cor_var_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

@@

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_landscape = fig_ind_landscape(no_compet_low_cor_var_df,
                                                            no_compet_low_cor_var_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

@@

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_landscape = fig_ind_landscape(no_compet_high_cor_var_df,
                                                             no_compet_high_cor_var_label,
                                                             n_bins = 17)

@@

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_landscape = fig_ind_landscape(compet_no_cor_var_df,
                                                        compet_no_cor_var_label,
                                                        n_bins = 22)

@@

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_landscape = fig_ind_landscape(compet_low_cor_var_df,
                                                         compet_low_cor_var_label,
                                                         n_bins = 17)

@@

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_landscape = fig_ind_landscape(compet_high_cor_var_df,
                                                          compet_high_cor_var_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_landscape
```

>>>>

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios,
                                time = 150, scenar_names = names(trait_scenarios)) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios,
               time = time) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, scenar_names))
}

@@

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    RA1090   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.90, 0.10, 0),
                          compet_weight = c(0,    0.90, 0.10)),
    RA2575   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    RA5050   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    RA7525   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    RA100100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

trait_scenar_names = c(
    RA1090 = "Growth = 10%\nCompet. = 90%",
    RA2575 = "Growth = 25%\nCompet. = 75%",
    RA5050 = "Growth = 50%\nCompet. = 50%",
    RA7525 = "Growth = 75%\nCompet. = 25%",
    RA100100 = "Growth = 100%\nCompet. = 100%"
)

@@

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_no_cor_var_df,
                                                           no_compet_no_cor_var_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

plot_no_compet_no_cor_df_ind_var_landscape
```

@@

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_low_cor_var_df,
                                                            no_compet_low_cor_var_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

plot_no_compet_low_cor_df_ind_var_landscape
```

@@

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_high_cor_var_df,
                                                             no_compet_high_cor_var_label,
                                                             n_bins = 17)

plot_no_compet_high_cor_df_ind_var_landscape
```

@@

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_var_landscape = fig_ind_landscape(compet_no_cor_var_df,
                                                        compet_no_cor_var_label,
                                                        n_bins = 22)

plot_compet_no_cor_df_ind_var_landscape
```

@@

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_var_landscape = fig_ind_landscape(compet_low_cor_var_df,
                                                         compet_low_cor_var_label,
                                                         n_bins = 17)

plot_compet_low_cor_df_ind_var_landscape
```

@@

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_var_landscape = fig_ind_landscape(compet_high_cor_var_df,
                                                          compet_high_cor_var_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_var_landscape
```
